---
title: "Data Exploration Assignment"
author: "Jennifer Grosz"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Relevant Libraries
```{r}
library(tidyverse)
library(vtable)
library(jtools)
library(estimatr)
library(haven)
library(car)
```

### Load Data Set
```{r}
mydata <- read_csv("../data/mydata.csv")
# look at vtable
vtable(mydata) 

mydata <- mydata %>%
  mutate(institution = factor(institution))
```
### Analyze Data Set
Variables in data set:
  * "unitid" - unique college ID (numeric)
* "institution" - name of college (character)
* "aggIndex" - index scores that have been standardized (subtract the mean and divide by the standard deviation) and then aggregated by college per month (numeric)
* "high_earning" - Dummy variable to distinguish between high_earning v. low earning colleges based on the mean of median graduate earnings ten years after graduation (numeric)
* "time_var" - incrementally increases over months (numeric)
* "CollegeScorecard" - Dummy variable to distinguish between index scores from before the College Scorecard was released and after it was released at the beginning of September 2015 (numeric)
* "time" - scaled variable that shows 1-unit change in decrease or increase around the date the college scorecard came out (numeric)


```{r}
# institution
institutions <- mydata %>% filter(!duplicated(institution)) %>%
  summarize(count=n()) # 1785 unique institutions in data set

# Summary Statistics for Aggregated index and time variable
summary(mydata[c("aggIndex", "time_var")]) 

# Standard Deviation
sd(mydata$aggIndex) # standard deviation is 0.5790659
# Correlation
# Check correlation between independent variables
cor(mydata[c("CollegeScorecard", "high_earning", "time_var")])
```


```{r}
hist(mydata$CollegeScorecard) # imbalanced histogram
hist(mydata$high_earning)
hist(mydata$time_var)
hist(mydata$aggIndex)

ggplot(mydata, aes(x = time_var, y = aggIndex, color = factor(high_earning))) + 
  geom_point() + 
  labs(title = "Aggregated Index Scores over Time",
       x = "Time",
       y = "Aggregated Index Scores",
       color = "high earning")
```

# Regression Model 1
```{r}
model <- lm(aggIndex ~ CollegeScorecard + high_earning 
            + time_var + CollegeScorecard*time_var + CollegeScorecard*high_earning, mydata)
export_summs(model, digits = 3, robust = TRUE)
```

```{r}
# Hypothesis test for if CollegeScorecard were to have 0 effect on index scores
linearHypothesis(model, "CollegeScorecard = 0", white.adjust = TRUE)
```


```{r}
# Graph of regression results for the effect of the CollegeScorecard on Aggregated Index Scores
effect_plot(model, pred = "CollegeScorecard", plot.points = TRUE)

# Regression results + differientatior high vs low earning college graduates:
ggplot(data=mydata, 
       aes(x=CollegeScorecard, y = aggIndex, 
           group= high_earning, 
           color=factor(high_earning))) + 
  geom_line() + 
  xlab("CollegeScorecard") + 
  ylab("Aggregate Index") + 
  scale_color_discrete(name = "high_earning", 
                        labels=c("low_earning", "high_earning"))


# Standardize residuals
unstandardizedResiduals <- resid(model)
standardizedResiduals <- ((unstandardizedResiduals - mean(unstandardizedResiduals))/ sd(unstandardizedResiduals))

# Standardize Predicted Values
unstandardizedPredicted <- predict(model)
standardizedPredicted <- ((unstandardizedPredicted - mean(unstandardizedPredicted)) /sd(unstandardizedPredicted))

# Check Normality Assumption with Graph
ggplot(data = mydata) +
  geom_histogram(mapping = aes(x = aggIndex), binwidth = 1) +
  xlab("Regression Standardized Residuals") 

# Check Constant Variance Assumption with Graph
ggplot(data = mydata, mapping = aes(x = standardizedPredicted, y = standardizedResiduals, color = factor(high_earning))) + 
  geom_point() +
  geom_smooth(method = "lm") +
  xlab("Fitted Values") + 
  ylab("StandardizedResiduals")+ 
  scale_color_discrete(name = '', labels=c("low_earning", "high_earning"))
```

#### Additional Regression Model
```{r}
# Other models explored
reg1 <- lm(aggIndex ~ CollegeScorecard*time_var, mydata)
primary_model <- model
export_summs(reg1, primary_model, digits = 3, robust = TRUE)
```


